### 2013-06-24 trunk/network-science/paper.tex

Then we move on the dynamic centrality, by expanding the often used model
for static network named Katz centrality[?], which is actually a generalized
version of eigenvalue centrality[?] which estimate the influence of a node in
social networks by counting the total number of walks between a pair of
node[?]. We try to combine the activity and the clasical centrality metric and
expect to define a new centrality model that is mode sensitive to immediate
effect.

@@

\begin{center} \begin{tikzpicture} \begin{axis}[ 
	thick,
	width=0.6\textwidth,
	x=1cm/4,
	xmax=10, ymax=1,
	axis line style=very thick,
	axis x line=bottom,
	axis y line=left,
	xlabel={$z$},
	ylabel={evolving activity},
] 
	\addplot[color=blue!50!black,samples=300,domain=-40:-0.001] {exp(ln(10)*(1/x))}; 
	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(100)*(1/x))}; 
	\addplot[color=red!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
	\end{axis} \end{tikzpicture} 
\end{center}

>>>>

Then we move on the dynamic centrality, by extending the often used model
for static network named Katz centrality\cite{katz1953new}, which is actually
a generalized version of eigenvalue centrality which estimate the influence
of a node in social networks by counting the total number of walks between a pair of
node. We try to combine the activity and the clasical centrality metric and
expect to define a new centrality model that is mode sensitive to immediate
effect.

@@

\begin{center} \begin{tikzpicture} \begin{axis}[ 
	thick,
	width=0.6\textwidth,
	x=1cm/4,
	xmax=10, ymax=1,
	axis line style=very thick,
	axis x line=bottom,
	axis y line=left,
	xlabel={$z$},
	ylabel={evolving activity},
] 
	\addplot[color=blue!50!black,samples=300,domain=-40:-0.001] {exp(ln(10)*(1/x))}; 
	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
	\addplot[color=red!50!black,samples=300,domain=-40:-0.001]
	{exp(ln(100000)*(1/x))}; 
	\legend{$\mu=10$,$\mu=10^3$,$\mu=10^6$};
	\end{axis} \end{tikzpicture} 
\end{center}
